\section{Implementation}
\label{sec:implementation}

\subsection{Data collection}
\label{sec:implementation/data_collection}

Foo!

\subsection{Usage mining}
\label{sec:implementation/usage_mining}

Foo!

\subsection{Presentation of results}
\label{sec:implementation/presentation}

After all references have been collected, a proper UI is still required to provide users easy access to these data that fulfills the requirements mentioned above.
To satisfy \cref{req2} and make our tool available in the usual working environment of users, we implement it as an extension to a popular IDE.
One of the most popular IDEs that support JavaScript, and the one with the highest annual growth, is Visual Studio Code.\footnote{\url{https://code.visualstudio.com/}}\footnote{Top IDE Index by Pierre Carbonnelle (2021): \url{https://pypl.github.io/IDE.html}}
As it also provides a comprehensive set of APIs for extension developers, we have decided to roll our tool out as a VS Code extension.

To support developers in answering the questions raised in \cref{sec:framework}, we have designed the following views for our extension:

\begin{enumerate}[label=(\roman*)]
	\item The \emph{dependency browser} allows to explore all downstream dependencies and, grouped for each dependency, all their references to the target package.
	\item The \emph{usage browser} displays all public package member and, grouped for each member, all dependencies and their references to this member.
	\item The \emph{CodeLens integration} provides quick access to a slice of the usage browser that is attached to the definition of each package member right in the source code editor.
\end{enumerate}

Both references and members are organized in a tree view reflecting the hierarchical structure of the original software repository.
In addition, we recognize the effort of browsing large lists of dependency data and encounter it by providing an ``I'm felling lucky'' button for every view that redirects the user to a random dependency resp. reference to gain a faster, unbiased impression of usage samples.

Foo!
